### 2021-03-09 paper_1.tex
start Experiments

>>>>

\subsubsection{Bayesian Inference With Contour Guidance}
Bayesian inference gives the possibility to calculate the probability that a 
pixel x may belong to a salient structure s. This probability is computed as:
$$ p(s|x) = \frac{p(s)p(x|s)}{p(s)p(x|s)+p(b)p(x|b) } $$
Where $ p(x|s) $ is the probability of a pixel belonging to a salient structure, 
$ p(x|b) $ is the probability that a pixel belongs to the background, $ p(b)=1-p(s) $,
finally $ p(s)=Sw $ represents the CBSP value. The implementation 
details are as follows.
\begin{enumerate}
    \item \emph{Predict the size of Potential Structure}: this procedure, through a binarization of the map obtained 
    from $ p(s) $, separates the salient structures from the background, all 
    through the use of a threshold. This threshold is calculated using the 
    local parameters (color, luminance, etc.), a percentage not greater than 
    50\% useful to denote the size of the salient structure, an initial weight 
    and finally two sets of pixels corresponding to the background and the 
    foreground (salient structure).
    \item \emph{Evaluate the Importance of Each Feature}: a feature is considered important 
    when the difference between the average pixel values of its 
    salient structure and those of the background is large enough, i.e. when \emph{$ w_i $} 
    takes on a satisfiable value.
    \item \emph{Calculate the Observation Likelihood}:in order to calculate the observed 
    probabilities, the different color channels \emph{($ f_{lum}, f_{rg}, f_{by}, f_{ed} $)} are used, 
    and the distribution functions $ p(x_i | S_{T_{opt}}) $ and $ p(x_i | B_{T_{opt}}) $ where $ S_{T_{opt}} $ 
    represents the set of pixels belonging to the structure salient, while 
    $ B_{T_{opt}} $ represents the set of pixels belonging to the background.
    $$ p(x|s) = \prod_{i \in {\{} f_{lum}, f_{rg}, f_{by}, f_{ed} {\}}} {(p(x_i | S_{T_{opt}}))^{w_i}} $$
    $$ p(x|b) = \prod_{i \in {\{} f_{lum}, f_{rg}, f_{by}, f_{ed} {\}}} {(p(x_i | B_{T_{opt}}))^{w_i}} $$
    \item \emph{Enhance the Salient Structure by Iterating}: the salient structures, at 
    each instant \emph{t}, with $ t = t_0,…, t_n $, are iteratively improved by applying 
    a median filter on each of them. In addition, the weight attributed to 
    the importance of each feature is changed. Finally, the CGVS model 
    will operate on a set of instants \emph{t}, thus forming the contour-guided 
    visual search.

\end{enumerate}
